---
output: github_document
title:  Generating a forecast from synthetic data
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

The first step (after installing the package) is to load the library `epismthr`, along with other packages as shown below.

```{r,echo=T,message=FALSE}
library(epismthr)
library(ggplot2)
library(dplyr)
library(fable)
```

Use the function `generate_cases()` to generate synthetic data, so that we can test the forecasting algorithm.

```{r,echo=T}
all_data <- generate_cases()
all_data
```


Get data from an earlier part of the epi curve in order to run a test.
```{r,echo=T}
test_data <- all_data %>%
  filter(Date <= as.Date("2023-10-24"))
```

Plot the SEIR model output and the generated data.
```{r,,echo=T}
ggplot(test_data,aes(x=Date,y=Cases))+
  geom_line()+
  geom_point()+
  geom_line(aes(y=Model),colour="red")+
  scale_x_date(date_breaks = "1 week", minor_breaks = "1 day",date_labels="%b %e")
```

Call the function `epi_forecast()` to generate the forecast, with a look-ahead duration of seven days. A list containing result data is returned.

```{r,echo=TRUE}
result <- epi_forecast(test_data,
                       look_ahead = 5)
```

First, we can plot the forecast.

```{r,echo=TRUE}
result$plot_fcast
```

Next, we can plot information on the overall fit.
```{r,echo=TRUE}
result$plot_comp
```

We can also access the forecast values and the confidence intervals.

```{r,echo=TRUE}
result$hilo
```


And display the training set accuracy measures.

```{r,echo=TRUE}
result$ts_accuracy
```
